---
name: Akhil Sadam
position: "Aerospace Department, University of Texas at Austin"
address: "2826 Cool River Loop, Round Rock, TX 78665"
photo: ./fonts/avatar2.png
www: akhilsadam.github.io
github: akhilsadam
scholar: 6G9FVRgAAAAJ
sc: lightwaveofficial
linkedin: akhil-sadam
email: akhil.sadam@utexas.edu
phone: 512-298-0307
aboutme: "simulation architect / automation engineer, independent game developer and composer."
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "000000"
output:
  vitae::awesomecv:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
library(vitae)
library(here)
library(vroom)
library(dplyr)
library(lubridate)
library(glue)
```
```{r setup2, include=FALSE}
here::here()
getwd()
here::i_am(path="_.R")
here::here()
```


# Positions

```{r}
jobs <- vroom(here::here("data", "jobs.csv"))

jobs |>
  arrange(desc(dates)) |> 
  detailed_entries(
    what = glue("{role} - {company}"),
    when = dates
)
```


# Qualifications

```{r}
edu <- vroom(here("data", "education.csv"))

detailed_entries(edu,
                 when = glue("{start_date}--{end_date}"),
                 what = glue("{degree} - {uni}"))

```

# Skills

```{r}
skills <- vroom(here::here("data", "skills.csv")) |>
  group_by(category) |>
  mutate(skill = paste(skill, collapse = ", ")) |>
  ungroup() |>
  unique()

skills |>
  detailed_entries(what = skill, with = category)
```

# Selected publications

```{r}
pubs <- vroom(here::here("data", "publications.csv"), delim = "\t")

pubs |>
  detailed_entries(
    what = publication
)
```

*See [here](https://scholar.google.com/citations?user=GqZm90IAAAAJ&hl=en) for a full list of my publications.*

# Selected software

```{r}
software <- vroom(here::here("data", "software.csv")) |>
  arrange(desc(when))

software |>
  detailed_entries(
    what = glue("{package} - {what}"), when = where
)
```

*Software that I have primarily developed has had over 30k downloads and been used/is used in multiple public health organisations such as the WHO and the ECDC. Software that I have managed the development of has had over 20k downloads. See [my GitHub](https://github.com/seabbs/) for more on my software output.*

# Research (Co-) Supervision

```{r research}
supervision <- vroom(here::here("data", "supervision.csv"))

supervision |>
  detailed_entries(
    what = glue("{who} - {what}"),
    when = when
)
```
# Teaching

```{r}
teaching <- vroom(here::here("data", "teaching.csv")) |>
  arrange(desc(when))

teaching |>
  detailed_entries(
    what = what, when = when
)
```


# Selected presentations

```{r}
presentations <- vroom(here::here("data", "presentations.csv")) |>
  arrange(desc(when))

presentations |>
  detailed_entries(
    what = with, when = when
)
```

*See the details, slides, and recordings of all my presentations [here](https://samabbott.co.uk/talks.html)*

# Service

```{r}
service <- vroom(here::here("data", "service.csv"))

service |>
  detailed_entries(what = glue("{type} - {details}"), when = when)
```
